What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-02-14 paper/main.tex
updated tllen def

\begin{definition}[Timeline Length]
    We define the timeline length of a regular expression $\tllen(A)$ recursively as follows
    \begin{align*}
        \tllen(\emptyset)   &= -\infty\\
        \tllen(\epsilon)        &= 0\\
        \tllen(a)           &= 1\\
        \tllen(A_1 A_2)     &= \tllen(A_1) + \tllen(A_2)\\
        \tllen(A_1 + A_2)   &= \max(\tllen(A_1), \tllen(A_2))\\
        \tllen(A^*)         &= 2\tllen(A) + 1
    \end{align*}
    We also extend this definition to $\omega$-regular expressions as follows
    \begin{align*}
        \tllen(A^\omega)    &= \tllen(A)\\
        \tllen(AB)          &= \tllen(A) + \tllen(B)\\
        \tllen(B_1 + B_2)   &= \max(\tllen(B_1), \tllen(B_2))
    \end{align*}
    This quantity $\tllen$ captures the length of the longest path in our timeline graph visualization.
\end{definition}

@@

\begin{figure}[h!]
    \centering
    \subfloat{{\includegraphics[width=6.5cm]{img/naive-ltl2tl-scatterplot-omit-big-values.png} }}%
    \quad % [\centering label 1]
    \subfloat{{\includegraphics[width=6.5cm]{img/star-height-scatter-plot.png}}}
    \caption{Visualization complexity metrics for formulas collected from Acacia \cite{RV10} and NASA's  AAC \cite{GCMTR16}}
    \label{fig:real-world}
\end{figure}

>>>>

\begin{definition}[Timeline Length]
    We define the timeline length of a regular expression $\tllen(A)$ recursively as follows
    \begin{align*}
        \tllen(\emptyset)   &= -\infty\\
        \tllen(\epsilon)        &= 0\\
        \tllen(a)           &= 1\\
        \tllen(A_1 A_2)     &= \tllen(A_1) + \tllen(A_2)\\
        \tllen(A_1 + A_2)   &= \max(\tllen(A_1), \tllen(A_2))\\
        \tllen(A^*)         &= \tllen(A) 
    \end{align*}
    We also extend this definition to $\omega$-regular expressions as follows
    \begin{align*}
        \tllen(A^\omega)    &= \tllen(A)\\
        \tllen(AB)          &= \tllen(A) + \tllen(B)\\
        \tllen(B_1 + B_2)   &= \max(\tllen(B_1), \tllen(B_2))
    \end{align*}
    This quantity $\tllen$ captures the length of the longest path in our timeline graph visualization.
\end{definition}

@@

\begin{figure}[h!]
    \centering
    \subfloat{{\includegraphics[width=6.5cm]{img/tllens-graph.png} }}%
    \quad % [\centering label 1]
    \subfloat{{\includegraphics[width=6.5cm]{img/star-height-graph.png}}}
    \caption{Visualization complexity metrics for formulas collected from Acacia \cite{RV10} and NASA's  AAC \cite{GCMTR16}}
    \label{fig:real-world}
\end{figure}
